\thispagestyle{empty}

\setcounter{page}{3}

\chapter*{Declaration of Authorship}

\vspace{1cm}

\noindent 
We, \textbf{Prateek Parmar, Saarthak Verma, Gaurav Mishra, Aditya Sharma}, declare that the work presented in ``\textbf{Adaptix}" is our own. We confirm that:

\medskip

\begin{itemize} 
    \item This work was completed entirely while in candidature for B.Tech. degree at Indian Institute of Information Technology, Lucknow.
    
    \medskip
    
    \item Where we have consulted the published work of others, it is always cited.
    
    \medskip
    
    \item Wherever we have cited the work of others, the source is always indicated. Except for the aforementioned quotations, this work is solely our work.
    
    \medskip
    
    \item We have acknowledged all major sources of information.
\end{itemize}

\vspace{2cm}

\noindent Signed:\\

\hspace{1.5cm}(Prateek) \hfill (Saarthak) \hfill (Gaurav) \hfill (Aditya)
\rule[0.5em]{33em}{0.5pt} 
 
\noindent Date:\\
\rule[0.5em]{33em}{0.5pt}

\cleardoublepage

\chapter*{CERTIFICATE}

This is to certify that the work entitled ``\textbf{Adaptix}" submitted by \textbf{Prateek Parmar, Saarthak Verma, Gaurav Mishra and Aditya Sharma} who got their name registered on \textbf{1st Dec 2021} for the award of B.Tech. degree at Indian Institute of Information Technology, Lucknow is absolutely based upon their own work under the supervision of \textbf{Dr. Niharika Anand}, Department of Computer Science, Indian Institute of Information Technology, Lucknow - 226002, U.P., India and that neither this work nor any part of it has been submitted for any degree/diploma or any other academic award anywhere before.  

\vspace{4cm}

\begin{center}
    Dr. Niharika Anand

    Department of Computer Science

    Indian Institute of Information Technology, Lucknow

    Pin - 226002, INDIA
\end{center}
